---
title: "Advanced R"
author: "Nate Olson"
date: "February 15, 2016"
output: html_document
---

## Data Structures
Quiz 
1. three properties of a vector: type, attributes, length  
2. four common types of atomic vectors: integer, double, boolean, character, two rare: complex and raw  
3. attributes - metadata, attr(x, "y") or attr(x,"y") <- value, access attributes using attributes()    
4. list and data frames can contain different types of data, vectors and matricies can only contain one data type
5. a list can contain a data frame as an element, a data frame cannot have a matrix as a column - can make a list array, data frame column as a matrix using df$x <- matrix() or I() such as data.frame(x = I(matrix()))

## Targeted reading
* Complex and raw vectors  
### list array  
* apply dimensions to a list to generate a list array
```{r}
l <- list(1:3, "a", TRUE, 1.0)
l
dim(l) <- c(2,2)
l
```
Good when you need to arrage a list in a grid like structure

### Special Columns
list
```{r}
df <- data.frame(x = 1:3)
df$y = list(1:2, 1:3, 1:4)
df
```

Using `I()` which add the `AsIs` class
```{r}
dfl <- data.frame(x = 1:3, y = I(list(1:2, 1:3, 1:4)))
dfl
```

Can have columns that are matrix or arrays as long as the number of rows are equal
```{r}
dfm <- data.frame(x = 1:3, y = I(matrix(1:9, nrow = 3)))
dfm
```


## Subsetting 
Quiz  
1. Subsetting with:   
    * Positive integer - selects elements  
    * Negative integer - remove elements  
    * logical vector - selects (TRUE), removes (FALSE) based on positions  
    * character vector - selects based on names  
2. `[` when applied to a list - sublist, `[[` sublist element, `$` sublist element by name  
3. use drop = FALSE when you want to maintain dimensions  
4. x[] <- fills all positions with 0, whereas x <- 0 assigns x to 0  
5. relabel categorical variables - lookup table, apply?  

### Lookup tables
```{r}
x <- c("m","f","u","f","f","m","m")
lookup <- c(m = "male", f = "female", u = NA)
unname(lookup[x])
c(m = "Known",f = "Known", u = "Unknown")[x]
```

## Functions
Quiz
1. three components of a function: name, arguments, body  
2. 11  
3. 1 + 2*3  
4. x <- c(1:10); mean(x, na.rm = TRUE)
5. no b is not evaluated  
6. infix function - between arguments; `% %` <- function(x,y){}, replacement function `name<-` 7. cleanup - on.exit()  

## OO field Guide
