---
title: "Untitled"
author: "Nate Olson"
date: "February 4, 2016"
output: html_document
---


```{r}
library(dplyr)
library(nycflights13)
data("flights")
filter(flights, year == 2013 | (year == 2013 & year == 2014))

```

Issues Transformation boolean operations figure `xor(x,y)`

Exercises
```{r}
flights %>% filter(month %in% 6:8)
flights %>% filter(dest %in% c("IAH","HOU"))
flights %>% filter(carrier %in% c("UA","AA","DL"))
flights %>% filter(dep_delay <= 0, arr_delay > 119)
```


Select helper functions
`starts_with("abc")`
`ends_with("xyz")`
`contains("ijk")`
`matches("(.)\\1")`
`num_range("x", 1:3)` matches x1, x2, x3

Rank functions
row_number()
min_rank()
dense_rank()
cume_dist()
present_rank()
ntile()

Number of distinct values
`n_distinct()`

Potentially add variable descriptors for flight data in transforma section


## Modeling 

```{r}
library(ggplot2)
library(dplyr)
library(mgcv)
library(splines)
library(broom)
```


```{r}
heights <- readRDS("~/r4ds/data/heights.RDS")
h <- lm(income~height, data = heights)
summary(h)
```

```{r}
ggplot(data = heights, mapping = aes(x = height, y = income)) +
  geom_point()
```
Note censoring

```{r}
cor(heights$height, heights$income, use = "na")
```

```{r}
ggplot(data = heights, mapping = aes(x = height, y = income)) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r}
augment(h)[1:5, ]
```

```{r}
heights2 <- augment(h, heights)
ggplot(data = heights2, mapping = aes(x = education, y = .resid)) +
  geom_point() +
  geom_smooth()
```

Modeling chapter still a work in progress


```{r}
library("quantreg")
ggplot(data = diamonds) +
  geom_point(mapping = aes(x = carat, y = price)) +
  geom_quantile(mapping = aes(x = carat, y = price),
                quantiles = c(0.05, 0.5, 0.95), 
                formula = y ~ poly(x, 2))
```

Suggestion with joins venn diagram add boolean logic
* inner_join (x & y)  
* left_join (x)
* full_join(x | y)
* right_join (y)

Strings
```{r}
library(stringr)
x <- c("apple", "banana", "pear")
str_view(x, "an")
x <- "a\\b"
writeLines(x)
x```



