---
title: "R4-DataSci-Lists"
author: "Nate Olson"
date: "February 10, 2016"
output: html_document
---

## List Basics
named list
```{r}
x_named <- list(a = 1, b = 2, c =3)
str(x_named)
```

list structures
```{r}
x1 <- list(c(1,2),c(3,4))
str(x1)
x2 <- list(list(1,2), list(3,4))
str(x2)
x3 <- list(1, list(2, list(3)))
str(x3)

```

subsetting `[]` extracts a sublist and `[[]]` extracts the sublist value, can access using `$`, same as `[[]]`

```{r}
df <- data.frame(a = 1:10, b = 21:30)
df["a"]
df[["a"]]
df$a
```

Generation of a multipurpose column summary function
```{r}
col_summary <- function(df, fun) {
  out <- vector("numeric", length(df))
  for (i in seq_along(df)) {
    out[i] <- fun(df[[i]])
  }
  out
}
col_summary(df, median)
col_summary(df, min)
```

Note the use of a function as an argument within a function

### Purrr
map function
list of map functions and output type
use the most specific map function, only use map() as a fallback
map arguments
1. list
2. function, character vector, or an integer vector
3. other arguments passed to the function everytime its called

map preserves names

Shortcuts
- splitting a dataframe
```{r}
library(purrr)
models <- mtcars %>% 
    split(.$cyl) %>% 
    map(function(df) lm(mpg~wt, data = df))
```

can replace `function(df) lm(mpg~wt, data = df)` with `~lm(mpg~wt, data = .)` for anonymous functions  

`.` used to represent current, .x and .y represent the first and second arguments.  

Extracting named components
```{r}
models %>% 
  map(summary) %>% 
  map_dbl(~.$r.squared)
```


Extracting named components directly
```{r}
models %>% 
  map(summary) %>% 
  map_dbl("r.squared")
```

numeric vector to extract elements 
```{r}
x <- list(list(1, 2, 3), list(4, 5, 6), list(7, 8, 9))
x %>% map_dbl(2)
```

Base R
lapply identical to map
apply simplifies output
vapply similar to apply but able to specify the output format 

### Handling Hierarchy
* extract with map and vector
* remove level using flatten
* flip with transpose


Transpose flipping a list inside out
```{r}
x <- list(
  x = list(a = 1, b = 3, c = 5),
  y = list(a = 2, b = 4, c = 6)
)
x %>% str()
x %>% transpose() %>% str()
```

### dealing with failure
`safely()` - takes a function does not return an error, returns list with result, and error (NULL if successful)

can transpose the output to get a list of errors

`possibly()` - similar to safely but always suceeds, returns a default value for a failure

Parallel maps
map2 - two lists
pmap() - takes a list of arguments
```{r}
library(purrr)
library(dplyr)
n <- list(1, 3, 5)
mu <- list(5, 10, -3)
sigma <- list(1, 5, 10)
args1 <- list(n, mu, sigma)
args1 %>% pmap(rnorm) %>% str()
```

Can store arguments in a data frame
```{r}
params <- dplyr::data_frame(mean = mu, sd = sigma, n = n)
params$result <- params %>% pmap(rnorm)
params
```

Covers intersection of dplyr and purrr in model fitting

### Invoking different functions
```{r}
f <- c("runif", "rnorm", "rpois")
param <- list(
  list(min = -1, max = 1), 
  list(sd = 5), 
  list(lambda = 10)
)
invoke_map(f, param, n = 5)
```

note here `n = 5` is passed with '...' to all functions

`frame_data` can be used to create matching pairs
```{r}
sim <- dplyr::frame_data(
  ~f,      ~params,
  "runif", list(min = -1, max = -1),
  "rnorm", list(sd = 5),
  "rpois", list(lambda = 10)
)
sim %>% dplyr::mutate(
  samples = invoke_map(f, params, n = 10)
)
```

### Walk
used when interested in side effects not return values, saving to disk or rendering output.

```{r}
x <- list(1, "a", 3)

x2 <- x %>% 
  walk(print)
x2
```

Saving plots to disk
```{r}
library(ggplot2)
plots <- mtcars %>% 
  split(.$cyl) %>% 
  map(~ggplot(., aes(mpg, wt)) + geom_point())
paths <- paste0(names(plots), ".pdf")

pwalk(list(paths, plots), ggsave, path = ".")
```

### Predicates
functions that return a TRUE/ FALSE
`keep` and `discard` work with predicates filters list
`head_while` and `tail_while` keep first and last element until first predicate is true  
`some()` predicate true for any element
`every()` predicate is true for all elements  
`detect()` and `detect_index()`  

Purrr predicate functions
`is_logical`, `is_integer`, `is_double`, `is_numeric`, `is_character`, `is_atomic`, `is_list`, `is_vector`, `is_null`


